Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
abstract

\begin{abstract}
While people naturally draw from diverse information sources in the course of routine decision-making, complementary support for managing diverse, heterogeneous data in digital Personal Information Management (PIM) tools remains poor.  In this paper, we present an exploratory initial investigation of ways to support user-driven, ad-hoc data integration in PIM tools, towards opening up for use the emerging ecosystem of structured data now available via APIs and structured data feeds on the Web.  We conducted an exploratory, sequential, mixed-method study, starting with two pre-studies focusing on blah and blah, finding that blahdyblah.  These observations led to the design of DataPalette, an interface for ``light-touch'' data integration that supported simple drag-and-drop and path-selection mechanisms for managing terminological and structurally heterogeneous data items.  Our lab study of DataPalette showed that users understood the interaction mechanisms introduced and the problems they were designed to solve, and that DesignPalette allowed them to make more carefully informed decisions and draw from more data sources while performing multidimensional subjective choice-based tasks.

>>>>

\begin{abstract}
While people naturally draw from diverse information sources in the course of routine decision-making, complementary support for managing diverse, heterogeneous data in digital Personal Information Management (PIM) tools remains poor.  In this paper, we present an exploratory initial investigation of user-driven, ad-hoc data integration approaches for PIM, towards enabling greater use of emerging ecosystem of structured data available on the Web.  We conducted an exploratory, sequential, mixed-method study, starting with two pre-studies focusing on the data integration needs and challenges, respectively, of effectively combining data from diverse Web-based structured data sources.  These observations led to the design of DataPalette, an interface for ``light-touch'' data integration that introduced drag-and-drop and path-selection mechanisms for managing collections of terminologically and structurally- heterogeneous data items.  Our lab study of DataPalette with actual data obtained from a selection of Web sites  showed that users understood the interaction mechanisms introduced and the problems they were designed to address, and that DesignPalette allowed them to make more carefully informed decisions and draw from more data sources while performing multidimensional subjective choice-based tasks.
